Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-24 manuscript/manuscript.tex
Minor changes in Methodology

On the variable density tesseroid problem we found two main error 
sources in the GLQ that should be addressed: (a) the distance between 
the tesseroid and the computation point, and (b) 
the variation of the density function.

The former one is also present in the homogeneous density tesseroid 
models, such as the one developed by \citet{Uieda2016}, and could be 
solved by applying a modified version of the adaptive discretization 
algorithm proposed by \citet{Li2011}.
Although for the latter we need to introduce a new density-based 
discretization algorithm that subdivides the tesseroid taking into 
account the variation of its density function.

@@

Lets assume an arbitrary \emph{original} tesseroid with boundary radii 
$R_1$ and $R_2$ and a density function $\rho(r')$, whose radial 
dimension can be written as $L_r = R_2 - R_1$.

@@

\begin{equation}
    \rho_n(r') = \frac{\rho(r') - \rho_1}{\rho_2 - \rho_1},
\end{equation}
\noindent where
\begin{equation}
    \rho_1 = \text{min}\{ \rho(r') \}, \quad
    \rho_2 = \text{max}\{ \rho(r') \} \quad
    \forall \, r' \in [R_1, R_2].
\end{equation}

@@

\noindent where the delta ratio $\delta$ is a predefined constant value 
and $L_r^\text{sm}/L_r$ is defined as the tesseroid size ratio.
Besides, $L_r^\text{sm}$ and $L_r$ are the radial dimensions of the 
tesseroid that is currently analysed and of the \emph{original} one, 
respectively.
On the first iteration, the former tesseroid corresponds to the 
\emph{original} one, so $L_r^\text{sm}/L_r$ is equal to one, but for 
future iterations this radial dimension will be computed as the 
difference of the top and bottom radii of the subdividing tesseroid.
The tesseroid size ratio is intended to reduce the number of probable 
unneeded discretizations and focus on discretizations that will 
significantly reduce the numerical error.
A big subdividing tesseroid with small maximum absolute difference would 
contribute more numerical error than a small subdividing tesseroid with 
higher maximum absolute difference.

Once the \emph{original} tesseroid is divided, we proceed to 
subsequently apply the same algorithm on every subdividing tesseroid.
We will start from equation \ref{eq:density-reference-line} defining a 
new linear function $\rho_l(r')$, an absolute difference with equation 
\ref{eq:density-abs-diff} and evaluate the discretization inequation 
\ref{eq:delta-density}, taking into account that now $R_1$ and $R_2$ 
are the radial boundaries of this smaller tesseroid.
If the inequation holds, the current tesseroid is discretized and the 
algorithm is then applied to the resulting subdividing tesseroids.

If on the contrary the inequation \ref{eq:delta-density} is not held, 
then the tesseroid will not be subdivided.
The same happens if the tesseroid radial dimension is bellow the 
threshold of 1mm.
On the first case due to the fact that no more discretizations are 
needed, and on the second one because smaller tesseroids will not 
introduce meaningful increases in the accuracy of the computation.
This two conditions guarantee that the algorithm is finite.
Once any of them is met and no more discretizations are carried out, 
every subdividing tesseroid is subjected to the modified adaptive 
discretization algorithm and then a second order GLQ must be applied in 
order to compute the gravitational field generated by it.

>>>>

On the variable density tesseroid problem we found two main error 
sources in the GLQ that should be addressed: (a) the distance between 
the tesseroid and the computation point, and (b) 
the variation of the density function.
The former one is also present in the homogeneous density tesseroid 
models, such as the one developed by \citet{Uieda2016}, and could be 
solved by applying a modified version of the adaptive discretization 
algorithm proposed by \citet{Li2011}.
Although for the latter we need to introduce a new density-based 
discretization algorithm that subdivides the tesseroid taking into 
account the variation of its density function.

@@

Lets assume an arbitrary \emph{original} tesseroid with boundary radii 
$R_1$ and $R_2$ and a density function $\rho(r')$, whose radial 
dimension is $L_r = R_2 - R_1$.

@@

\begin{equation}
    \rho_n(r') =
    \frac{\rho(r') - \rho_\text{min}}{\rho_\text{max} - \rho_\text{min}},
\end{equation}
\noindent where
\begin{equation}
    \rho_\text{min} = \text{min}\{ \rho(r') \}, \quad
    \rho_\text{max} = \text{max}\{ \rho(r') \} \quad
    \forall \, r' \in [R_1, R_2].
\end{equation}

@@

\noindent where the delta ratio $\delta$ is a predefined constant value and 
$L_r^\text{sm}/L_r$ is defined as the tesseroid size ratio, while 
$L_r^\text{sm}$ and $L_r$ are the radial dimensions of the tesseroid that is 
currently analysed and of the \emph{original} one, respectively.
On the first iteration, the former tesseroid corresponds to the 
\emph{original} one, so $L_r^\text{sm}/L_r$ is equal to one, but for 
future iterations this radial dimension will be computed as the 
difference of the top and bottom radii of the subdividing tesseroid, making 
$L_r^\text{sm}/L_r$ lower than one.
The tesseroid size ratio is intended to reduce the number of unneeded 
discretizations and focus on the ones that will significantly reduce the 
numerical error:
a big subdividing tesseroid with small maximum absolute difference would 
cause more relative numerical error than a small subdividing tesseroid with 
higher maximum absolute difference.

Once the \emph{original} tesseroid is discretized, we proceed to 
subsequently apply the same algorithm on every subdividing tesseroid.
We will start from equation \ref{eq:density-reference-line} defining a 
new linear function $\rho_l(r')$, an absolute difference with equation 
\ref{eq:density-abs-diff} and evaluate the discretization inequation 
\ref{eq:delta-density}, taking into account that now $R_1$ and $R_2$ 
are the radial boundaries of this smaller tesseroid.
If the inequation holds, the current tesseroid is discretized and the 
algorithm is subsequently applied to the resulting subdividing tesseroids.

If on the contrary the inequation \ref{eq:delta-density} is not held, 
then the tesseroid will not be discretized.
The same happens if the tesseroid radial dimension is bellow the 
threshold of 1mm.
On the first case due to the fact that no more discretizations are 
needed, and on the second one because smaller tesseroids will not 
introduce meaningful increases in the accuracy of the computation.
This two conditions guarantee that the algorithm is finite.
Once any of them is met and no more discretizations are carried out, 
every subdividing tesseroid is subjected to the modified adaptive 
discretization algorithm and then a second order GLQ will be applied in 
order to compute the gravitational field generated by it.
